---
title: "Billboard Hot 100 Archive"
---

This section covers Drake's historic run on the Billboard Hot 100 from his first entry in 2009 through 2021, containing **2,569 weekly chart observations** curated via [TidyTuesday](https://github.com/rfordatascience/tidytuesday/tree/master/data/2021/2021-09-14) and [Billboard's chart history](https://www.billboard.com/artist/drake/chart-history/).

::: {.stat-grid}
::: {.stat-card}
::: {.stat-number}
2,569
:::
::: {.stat-label}
Total Observations
:::
:::

::: {.stat-card}
::: {.stat-number}
234
:::
::: {.stat-label}
Distinct Songs
:::
:::

::: {.stat-card}
::: {.stat-number}
51
:::
::: {.stat-label}
Weeks at #1
:::
:::

::: {.stat-card}
::: {.stat-number}
301
:::
::: {.stat-label}
Top 10 Weeks
:::
:::
:::

## Career Chart Trajectory (2009–2021)

Every single weekly chart rank is plotted below. Drake has set records for both longevity and simultaneous multi-song saturation on the Hot 100.

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 10
#| fig-height: 5.8
#| dpi: 300

library(tidyverse)

drake_data <- read_csv("data/drake_billboard.csv", show_col_types = FALSE) |> 
  mutate(
    role = if_else(str_starts(performer, "Drake"), "Lead Artist", "Featured Artist")
  )

ggplot(drake_data, aes(x = week_date, y = week_position, color = role)) +
  geom_point(alpha = 0.42, size = 1.9) +
  geom_smooth(se = FALSE, method = "loess", span = 0.32, linewidth = 1.1) +
  scale_y_reverse(breaks = c(1, 10, 25, 50, 75, 100)) +
  scale_color_manual(values = c("Lead Artist" = "#1e40af", "Featured Artist" = "#ea580c")) +
  scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
  labs(
    title = "Drake on the Billboard Hot 100 (2009–2021)",
    subtitle = "Tracking 2,569 weekly positions across lead and featured tracks",
    x = "Year",
    y = "Billboard Hot 100 Rank (1 is top)",
    color = "Drake's Role",
    caption = "Source: TidyTuesday / Billboard.com (2,569 observations)"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", size = 16, color = "#0f172a"),
    plot.subtitle = element_text(color = "#475569", margin = margin(b = 12)),
    legend.position = "top",
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "#f1f5f9")
  )
```

## Billboard Historical Explorer

Search and filter all 2,569 chart appearances:

```{r}
#| echo: false
#| message: false
#| warning: false

library(DT)

drake_table <- drake_data |> 
  select(
    `Chart Date` = week_date,
    `Rank` = week_position,
    `Song Title` = song,
    `Performer Credit` = performer,
    `Peak Rank` = peak_position,
    `Weeks on Chart` = weeks_on_chart
  ) |> 
  arrange(desc(`Chart Date`), `Rank`)

datatable(
  drake_table,
  filter = "top",
  rownames = FALSE,
  class = "hover stripe compact",
  options = list(
    pageLength = 20,
    lengthMenu = c(10, 20, 50, 100),
    autoWidth = TRUE,
    scrollX = TRUE
  )
)
```
