---
title: "Chart & Track Explorer"
---

This tab puts control directly in your hands. Explore **2,569 weekly Billboard Hot 100 observations** across Drake's chart career (2009–2021).

### Interactive Exploration Tools:
- **Pull-down Menu:** Use the dropdown menu in the upper-left of the chart to instantly isolate **Lead Singles**, **Guest Features**, or view **All Tracks**.
- **Hover Details:** Hover over any data point to reveal the song name, chart date, weekly position, peak rank, and collaboration credits.
- **Click-and-Drag Zoom:** Click and drag a box over any cluster of points (such as the Summer 2018 *Scorpion* surge) to zoom in. Double-click anywhere to reset.

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 10
#| fig-height: 6

library(tidyverse)
library(plotly)

drake_data <- read_csv("data/drake_billboard.csv", show_col_types = FALSE) |> 
  mutate(
    role = if_else(str_starts(performer, "Drake"), "Lead Artist", "Featured Artist"),
    tooltip = str_c(
      "<b>", song, "</b><br>",
      "Role: ", role, "<br>",
      "Credit: ", performer, "<br>",
      "Date: ", week_date, "<br>",
      "Rank: #", week_position, "<br>",
      "Peak: #", peak_position, "<br>",
      "Weeks on Chart: ", weeks_on_chart
    )
  )

lead_data <- drake_data |> filter(role == "Lead Artist")
feat_data <- drake_data |> filter(role == "Featured Artist")

p <- plot_ly() |> 
  add_trace(
    data = lead_data,
    x = ~week_date,
    y = ~week_position,
    name = "Lead Artist (1,484)",
    type = "scatter",
    mode = "markers",
    text = ~tooltip,
    hoverinfo = "text",
    marker = list(size = 5.5, color = "#1e40af", opacity = 0.55)
  ) |> 
  add_trace(
    data = feat_data,
    x = ~week_date,
    y = ~week_position,
    name = "Featured Artist (1,085)",
    type = "scatter",
    mode = "markers",
    text = ~tooltip,
    hoverinfo = "text",
    marker = list(size = 5.5, color = "#ea580c", opacity = 0.55)
  ) |> 
  layout(
    title = list(
      text = "<b>Interactive Billboard Hot 100 Explorer (2,569 Observations)</b>",
      font = list(size = 15)
    ),
    xaxis = list(title = "Chart Date", showgrid = TRUE, gridcolor = "#f1f5f9"),
    yaxis = list(title = "Hot 100 Rank (1 is top)", autorange = "reversed", showgrid = TRUE, gridcolor = "#f1f5f9"),
    hoverlabel = list(bgcolor = "white", font = list(size = 12)),
    legend = list(orientation = "h", x = 0.35, y = 1.12),
    updatemenus = list(
      list(
        type = "dropdown",
        direction = "down",
        x = 0.0,
        y = 1.15,
        showactive = TRUE,
        buttons = list(
          list(
            method = "restyle",
            args = list("visible", list(TRUE, TRUE)),
            label = "View: All Tracks (2,569)"
          ),
          list(
            method = "restyle",
            args = list("visible", list(TRUE, FALSE)),
            label = "View: Lead Singles Only (1,484)"
          ),
          list(
            method = "restyle",
            args = list("visible", list(FALSE, TRUE)),
            label = "View: Guest Features Only (1,085)"
          )
        )
      )
    )
  )

p
```

---

## Searchable Billboard Database

Filter and sort through every individual observation. Use the column search boxes to look up specific tracks (e.g., "God's Plan", "In My Feelings", "Hotline Bling") or view all songs that peaked at #1.

```{r}
#| echo: false
#| message: false
#| warning: false

library(DT)

explorer_table <- drake_data |> 
  select(
    `Chart Date` = week_date,
    `Rank` = week_position,
    `Song Title` = song,
    `Role` = role,
    `Performer Credit` = performer,
    `Peak Rank` = peak_position,
    `Weeks on Chart` = weeks_on_chart
  ) |> 
  arrange(desc(`Chart Date`), `Rank`)

datatable(
  explorer_table,
  filter = "top",
  rownames = FALSE,
  class = "hover stripe compact",
  options = list(
    pageLength = 15,
    lengthMenu = c(10, 15, 25, 50, 100),
    autoWidth = TRUE,
    scrollX = TRUE
  )
)
```
