---
title: "Drake: Billboard Records & Streaming Dominance"
---

Welcome to the Drake music analytics project. This site examines Drake's historic career through **thousands of data points**—combining **2,569 weekly Billboard Hot 100 observations** from [TidyTuesday](https://github.com/rfordatascience/tidytuesday/tree/master/data/2021/2021-09-14) with over **140 billion Spotify streams** from [kworb.net](https://kworb.net/spotify/artist/3TVXtAsR1Inumwj472S9r4_songs.html) and track telemetry from [Songstats](https://songstats.com/track/ul9j1yr4/drake).

::: {.stat-grid}
::: {.stat-card}
::: {.stat-number}
2,569
:::
::: {.stat-label}
Billboard Chart Observations
:::
:::

::: {.stat-card}
::: {.stat-number}
140.7B
:::
::: {.stat-label}
Total Spotify Streams
:::
:::

::: {.stat-card}
::: {.stat-number}
51
:::
::: {.stat-label}
Weeks at #1
:::
:::

::: {.stat-card}
::: {.stat-number}
547
:::
::: {.stat-label}
Spotify Charted Songs
:::
:::
:::

## Career Chart Trajectory (2,569 Observations)

The visualization below is constructed from **2,569 individual weekly chart appearances** by Drake on the Billboard Hot 100 between 2009 and 2021. Every point captures a single week on the chart, colored by whether Drake was the primary lead artist or a featured collaborator. The trend lines illustrate how Drake maintained an unbroken top-tier chart presence across more than a decade.

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 10
#| fig-height: 5.6
#| dpi: 300

library(tidyverse)

drake_bb <- read_csv("data/drake_billboard.csv", show_col_types = FALSE) |> 
  mutate(
    role = if_else(str_starts(performer, "Drake"), "Lead Artist", "Featured Artist")
  )

ggplot(drake_bb, aes(x = week_date, y = week_position, color = role)) +
  geom_point(alpha = 0.42, size = 1.9) +
  geom_smooth(se = FALSE, method = "loess", span = 0.32, linewidth = 1.1) +
  scale_y_reverse(breaks = c(1, 10, 25, 50, 75, 100)) +
  scale_color_manual(values = c("Lead Artist" = "#1e40af", "Featured Artist" = "#ea580c")) +
  scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
  labs(
    title = "Drake on the Billboard Hot 100 (2009–2021)",
    subtitle = "Tracking 2,569 weekly positions across lead and featured releases",
    x = "Year",
    y = "Billboard Hot 100 Rank (1 is top)",
    color = "Drake's Role",
    caption = "Source: TidyTuesday / Billboard.com Archive (2,569 observations)"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", size = 16, color = "#0f172a"),
    plot.subtitle = element_text(color = "#475569", margin = margin(b = 12)),
    legend.position = "top",
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "#f1f5f9")
  )
```

::: {style="display: flex; gap: 0.75rem; margin-bottom: 2rem;"}
<a href="explorer.html" class="btn btn-primary btn-sm">Explore Interactive Billboard Data &rarr;</a>
<a href="features.html" class="btn btn-outline-primary btn-sm">Read Story: The Feature Effect &rarr;</a>
:::

---

## Spotify Streaming Dominance

Alongside his historical Billboard dominance, Drake is one of the most-streamed artists in Spotify history, accumulating **over 140 billion streams**. 

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 9.5
#| fig-height: 4.8
#| dpi: 300

library(tidyverse)
library(scales)

songs_data <- read_csv("data/kworb_songs.csv", show_col_types = FALSE)

top_10_spotify <- songs_data |> 
  slice_head(n = 10) |> 
  mutate(title = fct_reorder(title, streams))

ggplot(top_10_spotify, aes(x = streams / 1e9, y = title, fill = role)) +
  geom_col(width = 0.7) +
  geom_text(
    aes(label = str_c(round(streams / 1e9, 2), "B")),
    hjust = -0.15,
    size = 3.6,
    fontface = "bold",
    color = "#1e293b"
  ) +
  scale_x_continuous(
    labels = label_number(suffix = "B"),
    expand = expansion(mult = c(0, 0.16))
  ) +
  scale_fill_manual(values = c("Lead Artist" = "#1e40af", "Featured Artist" = "#ea580c")) +
  labs(
    title = "Top 10 Drake Tracks on Spotify by Total Streams",
    subtitle = "Streaming figures in billions; comparing lead tracks and featured appearances",
    x = "Streams (Billions)",
    y = NULL,
    fill = "Drake's Role",
    caption = "Source: kworb.net Spotify Songs Tracker"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold", size = 15, color = "#0f172a"),
    plot.subtitle = element_text(color = "#475569", margin = margin(b = 10)),
    legend.position = "top",
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_line(color = "#e2e8f0")
  )
```

[Browse Full 500-Song Spotify Catalog &rarr;](spotify.html){.btn .btn-outline-primary .btn-sm}

---

## Featured Cross-Platform Track

Track-level telemetry from [Songstats](https://songstats.com/track/ul9j1yr4/drake) illustrates global DSP footprint:

::: {.track-card}
<img src="https://i.scdn.co/image/ab67616d00001e02f0c843a56521f2be4d0d10e2" alt="Drake Track Artwork" class="track-art" />

<div>
  <h4 style="margin-top:0;">Track: "Drake"</h4>
  <p style="margin-bottom:0.4rem; color:#475569;"><strong>Artists:</strong> Alsago & Slight Shady &bull; <strong>Release Date:</strong> March 13, 2026</p>
  <p style="margin-bottom:0.4rem; color:#475569;"><strong>ISRC:</strong> <code>CAHQJ2683690</code> &bull; <strong>Distribution:</strong> 184 Countries across Spotify, Apple Music, Deezer, Amazon & Tidal</p>
  <p style="margin-bottom:0;"><a href="songstats.html" class="btn btn-outline-primary btn-sm">View Songstats Track &rarr;</a> <a href="https://songstats.com/track/ul9j1yr4/drake" target="_blank" class="btn btn-outline-secondary btn-sm">Open on Songstats.com &nearr;</a></p>
</div>
:::
