---
title: "Spotify Streaming Analytics"
---

This section analyzes Drake's global streaming footprint on Spotify based on catalog data tracked by [kworb.net](https://kworb.net/spotify/artist/3TVXtAsR1Inumwj472S9r4_songs.html). Drake is one of the most-streamed artists in Spotify history, having amassed over **140 billion streams** across 547 charted songs.

::: {.stat-grid}
::: {.stat-card}
::: {.stat-number}
140.7B
:::
::: {.stat-label}
Total Spotify Streams
:::
:::

::: {.stat-card}
::: {.stat-number}
65.9M
:::
::: {.stat-label}
Daily Streams
:::
:::

::: {.stat-card}
::: {.stat-number}
547
:::
::: {.stat-label}
Catalog Tracks
:::
:::

::: {.stat-card}
::: {.stat-number}
4.48B
:::
::: {.stat-label}
#1 Song (One Dance)
:::
:::
:::

## Catalog Stream Distribution

Drake's catalog spans solo releases, lead tracks with guest artists, and guest features on other artists' tracks. The data demonstrates how guest features played a massive role in building his cumulative streaming audience.

```{r}
#| echo: false
#| message: false
#| warning: false

library(tidyverse)
library(knitr)

summary_data <- read_csv("data/kworb_summary.csv", show_col_types = FALSE)

summary_data |> 
  kable(
    col.names = c("Metric", "Total", "As Lead", "Solo", "As Feature (*)"),
    align = c("l", "r", "r", "r", "r")
  )
```

## Top 15 Most Streamed Songs

The chart below shows Drake's 15 most-streamed songs on Spotify of all time, colored by whether he was the lead artist or a featured performer.

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 9.5
#| fig-height: 6
#| dpi: 300

library(tidyverse)
library(scales)

songs_data <- read_csv("data/kworb_songs.csv", show_col_types = FALSE)

top_15 <- songs_data |> 
  slice_head(n = 15) |> 
  mutate(
    title = fct_reorder(title, streams)
  )

ggplot(top_15, aes(x = streams / 1e9, y = title, fill = role)) +
  geom_col(width = 0.72) +
  geom_text(
    aes(label = str_c(round(streams / 1e9, 2), "B")),
    hjust = -0.15,
    size = 3.5,
    fontface = "bold",
    color = "#334155"
  ) +
  scale_x_continuous(
    labels = label_number(suffix = "B"),
    expand = expansion(mult = c(0, 0.15))
  ) +
  scale_fill_manual(values = c("Lead Artist" = "#1e40af", "Featured Artist" = "#ea580c")) +
  labs(
    title = "Top 15 Most-Streamed Drake Songs on Spotify",
    subtitle = "All-time streams in billions; comparison of lead tracks vs. features",
    x = "Total Streams (Billions)",
    y = NULL,
    fill = "Artist Role",
    caption = "Source: kworb.net Spotify Artist Songs Tracker"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold", size = 15, color = "#0f172a"),
    plot.subtitle = element_text(color = "#475569", margin = margin(b = 10)),
    legend.position = "top",
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_line(color = "#e2e8f0")
  )
```

## Top 10 Daily Stream Velocity

Streaming velocity indicates songs that continue to experience high daily playback today.

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 9.5
#| fig-height: 5
#| dpi: 300

top_daily <- songs_data |> 
  arrange(desc(daily)) |> 
  slice_head(n = 10) |> 
  mutate(title = fct_reorder(title, daily))

ggplot(top_daily, aes(x = daily / 1e6, y = title, fill = role)) +
  geom_col(width = 0.72) +
  geom_text(
    aes(label = str_c(round(daily / 1e6, 2), "M/day")),
    hjust = -0.15,
    size = 3.5,
    fontface = "bold",
    color = "#334155"
  ) +
  scale_x_continuous(
    labels = label_number(suffix = "M"),
    expand = expansion(mult = c(0, 0.18))
  ) +
  scale_fill_manual(values = c("Lead Artist" = "#2563eb", "Featured Artist" = "#f97316")) +
  labs(
    title = "Top 10 Drake Tracks by Daily Spotify Streams",
    subtitle = "Current daily streaming pace in millions of plays per day",
    x = "Daily Streams (Millions)",
    y = NULL,
    fill = "Artist Role",
    caption = "Source: kworb.net Spotify Artist Songs Tracker"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold", size = 15, color = "#0f172a"),
    plot.subtitle = element_text(color = "#475569", margin = margin(b = 10)),
    legend.position = "top",
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_line(color = "#e2e8f0")
  )
```

## Complete Spotify Songs Catalog (Top 500)

Use the table below to search and sort Drake's top 500 songs on Spotify by total streams, daily streams, or role.

```{r}
#| echo: false
#| message: false
#| warning: false

library(DT)

display_table <- songs_data |> 
  select(
    Rank = rank,
    `Song Title` = title,
    `Role` = role,
    `All-Time Streams` = streams,
    `Daily Streams` = daily
  )

datatable(
  display_table,
  filter = "top",
  rownames = FALSE,
  class = "hover stripe compact",
  options = list(
    pageLength = 20,
    lengthMenu = c(10, 20, 50, 100),
    autoWidth = TRUE,
    scrollX = TRUE
  )
) |> 
  formatCurrency(
    columns = c("All-Time Streams", "Daily Streams"),
    currency = "",
    digits = 0
  )
```
